\hspace{-1mm}{J-ReCoVer}:~Java~Reducer~Commutativity~Verifier\thanks{The work was supported by the Minister of Science and Technology of Taiwan project 106-2221-E-001-009-MY3 and the Czech Science Foundation project 17-12465S.}

### 2019-08-26 draft.tex
final version
Minor change of language in the acknowledgement

\title{\hspace{-1mm}{J-ReCoVer}:~Java~Reducer~Commutativity~Verifier\thanks{The
work was supported by the Minister of Science and Technology of Taiwan project 106-2221-E-001-009-MY3 and Czech Science Foundation project
17-12465S.}}

@@

The command $s_2$ can be viewed as a function $F$ that reads the values of all variables and the current input before executing $s_2$ and outputs the values of all variables after $s_2$. The loop body $s_2$ contains no nested loop structure. Hence, a bounded summary in quantifier-free linear integer arithmetic is sufficient~for~describing~$F$.

>>>>

\title{\hspace{-1mm}{J-ReCoVer}:~Java~Reducer~Commutativity~Verifier\thanks{The
work was supported by the Minister of Science and Technology of Taiwan project
106-2221-E-001-009-MY3 and the Czech Science Foundation project
17-12465S.}}

@@

The command $s_2$ can be viewed as a function $F$ that reads the values of all variables and the current input before executing $s_2$ and outputs the values of all variables after $s_2$. Note that $s_2$ contains no nested loop structure. Hence, a bounded summary in quantifier-free linear integer arithmetic is sufficient~for~describing~$F$.
